### 2022-07-11 Article.tex
Добавлена английская часть от прошлой статьи, как образец.

%Нумерация формул относительно секции
\counterwithin*{equation}{section}
\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
%изменение шрифта в заголовке секции
%\makeatletter
%
%\renewcommand\section{
%	\@startsection{section}
%					{1}
%					{\z@}%
%					{-3.5ex \@plus -1ex \@minus -.2ex}%
%					{-1em}%
%					{\normalfont\normalsize\bfseries}
%}
%
%\makeatother

@@

	\end{thebibliography}
\end{document}

>>>>

%Нумерация формул относительно секции
\counterwithin*{equation}{section}
\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}

%изменение шрифта в заголовке секции
\makeatletter
%
%\renewcommand\section{
%	\@startsection{section}
%					{1}
%					{\z@}%
%					{-3.5ex \@plus -1ex \@minus -.2ex}%
%					{-1em}%
%					{\normalfont\normalsize\bfseries}
%}
\renewcommand{\@biblabel}[1]{#1. \hfil}
\makeatother

@@

	\end{thebibliography}

	\newpage

	\begin{center}
		\bf \large Bifurcations of equilibrium positions of a Hamiltonian system in cases of double Raman third-order resonance
	\end{center}
	\begin{center}
		\bf Kholostova O.V., Safonov A.I.
	\end{center}

	Kholostova Olga Vladimirovna, Moscow Aviation Institute (National Research University),  Volokolamskoe shosse, 4, Moscow, 125993, Russia, professor

	e-mail: kholostova\_o@mail.ru,  tel.  +7(499)1584466

	Safonov Alexey Igorevich, JSC ”NPF ”Infosistem-35”, 3rd Mytischinskaya st. 16, bld. 37, Moscow , 129626, Russia, first category programmer-engineer

	\section*{Abstract}

	The motion of a near-autonomous time-periodic two-degree-of-freedom Hamil-tonian system is considered in a neighborhood of the trivial equilibrium position being stable in the linear approximation. The system is assumed to implement two Raman third-order resonances being strong and weak. In this case, the frequencies of small oscillations are also related by the fourth-order resonant ratio. In the complete nonlin-ear system, this equilibrium position is unstable. By the perturbation theory methods, normalization of the Hamiltonian of perturbed motion is carried out in the members up to the fourth order inclusive with respect to disturbance, taking into account the existing resonances. The approximate (model) the system depending on three parame-ters is considered under the assumption that the coefficients of terms corresponding to the fourth-order resonance are small. By means of analytical and graphical methods, the issue of the existence and number of equilibrium positions of the model system is obtained. In the space of parameters of the problem, the domains are identified in which the number of equilibrium positions of the model system can vary from zero to five. As an application, the problem of motion of a dynamically symmetric satellite (modeled by a rigid body) about the center of mass in the central Newtonian gravita-tional field on the orbit with small eccentricity is considered. The motion of a satellite is studied in the neighborhood of its periodic motion generating from the hyperboloi-dal precession on a circular orbit. For parameter values corresponding to the multiple Raman third-order resonance, the coefficients of the normal forms of the model sys-tem are found. It is shown that there are three equilibrium points in this system, two of which are unstable and the third stable in the linear approximation. (292)

	{\bf Keywords:} Hamiltonian system, multiple Raman resonance, dynamically symmetric satellite, hy-perboloidal precession.

	\renewcommand{\refname}{References}

		\bibitem{} Kunicyn A.L. Differencial'nye uravnenija, 1971, vol. 7, no. 9, pp. 1704-1706.

		\bibitem{} Khazina G.G. Certain stability questions in the presence of resonances, J. of ap-plied mathematics and mechanics, 1974, vol. 38, Issue 1, pp. 43-51.

		\bibitem{} Kunitsyn A.L., Medvedev S.V. On stability in the presence of several resonances, J. of applied mathematics and mechanics, 1977, vol. 41, no. 3, pp. 419-426.

		\bibitem{} Kunitsyn A.L., Tashimov L.T. Nekotorye zadachi ustoichivosti nelineinykh rezo-nansnykh system,  Alma-Ata, Gylym, 1990, 196 p.

		\bibitem{} Khazin L.G. Ob ustoichivosti polozheniya ravnovesiya gamil'tonovykh sistem dif-ferentsial'nykh uravnenii (Vzaimodeistvie rezonansov tret'ego poryadka), Institut prikladnoi matematiki AN SSSR, preprint no. 133, Moscow, 1981, 20 p.

		\bibitem{} Khazin L.G. Interaction of third-order resonances in problems of the stability of hamiltonian systems,  J. of applied mathematics and mechanics, 1984, vol. 48, Is-sue 3, pp. 356-380.

		\bibitem{} Markeev A.P. On a Multiple Resonance in Linear Hamiltonian Systems, Doklady Physics, 2005, vol. 50, no. 5,  pp. 278-282.

		\bibitem{} Markeyev A.P. Multiple parametric resonance in Hamilton systems, J. of applied mathematics and mechanics, 2006, vol. 70, no. 2, pp. 176-194.

		\bibitem{} Markeev A.P. Lineinye gamil'tonovy sistemy i nekotorye zadachi ob ustoichi-vosti dvizheniya sputnika otnositel'no tsentr mass, Moscow – Izhevsk, Institut komp'yuternykh issledovanii, 2009, 396 p.

		\bibitem{} Markeev A.P. On One Special Case of Parametric Resonance in Problems of Ce-lestial Mechanics, Astronomy Letters,  200, vol. 31, no.5, pp. 350-356.

		\bibitem{} Markeev A.P.  Multiple Resonance in One Problem of the Stability of the Mo-tion of a Satellite Relative to the Center of Mass, Astronomy Letters,  2005, vol. 31, no. 9, pp. 627-633.

		\bibitem{} Kholostova O.V. Nelineinaya dinamika, 2012, vol. 8, no. 2, pp. 267-288.

		\bibitem{} Kholostova O.V.  Nelineinaya dinamika,  2015, vol. 11, no. 4, pp. 671-683.

		\bibitem{} Kholostova O. Stability of triangular libration points in a planar restricted ellip-tic three body problem in cases of double resonances, International Journal of Non-Linear Mechanics, 2015, vol. 73, pp. 64-68.

		\bibitem{} Kholostova O.V. Zadachi dinamiki tverdykh tel s vibriruyushchim podvesom,  Moscow– Izhevsk, Institut komp'yuternykh issledovanii, 2016, 308 p.

		\bibitem{} Kholostova O.V. Trudy XI Mezhdunarodnoi Chetaevskoi konferentsii. T. 2. Sektsiya 2. Ustoichivost',  Kazan',  KNITU-KAI, 2017,  pp. 222-229.

		\bibitem{} Safonov A.I., Kholostova O.V. Vestnik Udmurtskogo universiteta. Matematika. Mekhanika. Komp'yuternye nauki, 2016, vol. 26, no. 3, pp. 418-438.

		\bibitem{} Beletskij V.V. Dvizhenie sputnika otnositel'no centra mass v gravitacionnom pole, Moscow: Izd-vo MGU, 1975, 308 p.

		\bibitem{} Duboshin G.N.  Bjulleten’ ITA AN SSSR, 1960, no. 7, pp. 511-520.

		\bibitem{} Chernous’ko F.L. On the stability of regular precession of a satellite, J. of ap-plied mathematics and mechanics, 1964, vol. 28, no. 1, pp. 181-184.

		\bibitem{} Sarychev V.A. Kosmicheskie isssledovanija, 1965, vol. 3, no. 5, pp. 667-673
	\end{thebibliography}
\end{document}
